---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sRdpData

<!-- badges: start -->
[![](https://cranlogs.r-pkg.org/badges/grand-total/sRdpData)]
<!-- badges: end -->

The goal of sRdpData is to provide you with easy, programmatic access to data on all self-determination groups and organizations, the countries that they are challenging, their start and end years, and their use of violent and non-violent tactics. This package is part of the [Strategies of Resistance Data Project](http://www.kathleengallaghercunningham.com/data-projects.html). 

## Installation

You can install the development version of sRdpData from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("hgoers/sRdpData")
```

## Access group- and organization-level data for all years between 1960 and 2005

```{r}
library(sRdpData)

# Access organization-level data
srdp_orgs() # In organization-year dyads, or
srdp_orgs(wide = TRUE) # At the organization-level

# Access group-level data in much the same way
srdp_groups() # In group-year dyads, or
srdp_groups(wide = TRUE) # At the group-level
```

## Get annual data on groups' use of tactics

```{r}
library(sRdpData)

srdp_tactics()
```

## See how groups and organizations have changed over time

```{r}
library(sRdpData)
library(tidyverse)

srdp_orgs() %>% 
  group_by(year) %>% 
  summarise(n = n()) %>% 
  ggplot(aes(x = year, y = n)) +
  geom_line() + 
  theme_minimal() + 
  labs(title = "Number of organizations active each year, 1960-2005",
       x = "Year",
       y = NULL)
```
